\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-16 doc/mlsys_paper/paper.tex
more compact acknowledgements, as we are running out of space
make more room by slightly shrinking the code figure

\begin{figure}[!tb]
\hrule\vspace*{0.3ex}
\begin{minted}[fontsize=\small]{c++}
class LinearRegressionFunction {
 public:
  // Construct the LinearRegressionFunction with the given data
  LinearRegressionFunction(arma::mat& X, arma::vec& y) : X(X), y(y) {}

  // Compute the objective function
  double Evaluate(const arma::mat& theta) {
    return std::pow(arma::norm(y - X * theta), 2.0);
  }
  // Compute the gradient and store in 'gradient'
  void Gradient(const arma::mat& theta, arma::mat& gradient) {
    gradient = -2 * X.t() * (y - X * theta);
  }
 private:
  arma::mat& X; arma::vec& y;
};
\end{minted}
\hrule\vspace*{0.3ex}
\caption
  {
  Implementation of objective and gradient functions for linear regression,
  to be used by optimizers in \texttt{ensmallen}.
  The types {\tt arma::mat} and {\tt arma::vec} are 
  matrix and vector types from Armadillo~\cite{sanderson2016armadillo}.
  }
\label{fig:LinearRegressionFunction}
\end{figure}

@@

\subsubsection*{Acknowledgements}

The development team of {\tt ensmallen} does not include just the authors named
here but also a long list of other contributors.  See
\url{https://www.ensmallen.org/about.html} for more information.
% TODO: that URL may change

>>>>

\begin{figure}[!tb]
\hrule\vspace*{0.5ex}
\begin{adjustbox}{scale={0.95}{0.90}}
\begin{minipage}{\textwidth}
\begin{minted}[fontsize=\small]{c++}
class LinearRegressionFunction {
 public:
  // Construct the LinearRegressionFunction with the given data
  LinearRegressionFunction(arma::mat& X, arma::vec& y) : X(X), y(y) {}

  // Compute the objective function
  double Evaluate(const arma::mat& theta) {
    return std::pow(arma::norm(y - X * theta), 2.0);
  }
  // Compute the gradient and store in 'gradient'
  void Gradient(const arma::mat& theta, arma::mat& gradient) {
    gradient = -2 * X.t() * (y - X * theta);
  }
 private:
  arma::mat& X; arma::vec& y;
};
\end{minted}
\end{minipage}
\end{adjustbox}
\vspace*{0.5ex}\hrule\vspace*{0.5ex}
\caption
  {
  Implementation of objective and gradient functions for linear regression,
  used by optimizers in \texttt{ensmallen}.
  The types {\footnotesize\tt arma::mat} and {\footnotesize\tt arma::vec}
  are matrix and vector types
  from Armadillo~\cite{sanderson2016armadillo}.
  }
\label{fig:LinearRegressionFunction}
\end{figure}

@@

\subsubsection*{Acknowledgements}
\vspace*{-0.5em}

We would like to thank the many contributors to {\tt ensmallen},
who are listed on the associated website.

% The development team of {\tt ensmallen} does not include just the authors named
% here but also a long list of other contributors.  See
% \url{https://www.ensmallen.org/about.html} for more information.
% % TODO: that URL may change
